The Driving Forces of API Evolution

### 2015-05-25 thesis/paper.tex
meth table

\section{Methodology} \label{methodology}
%Intro and summary
This study has been conducted using the case study methodology \cite{runeson2009guidelines}. Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis. The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context. The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case, robson2002real, runeson2009guidelines, yin2013case}. An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}. An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of drivers of API change and that input from the industry is vital to the success of the research.

The study was conducted in two major phases \cite{andersson2007spiral}. The aim of the first phase was to generate hypotheses and to formulate clear research questions. This was achieved by using a data-driven approach to analysing the code and documentation. The second phase included analysis of the interviews, during which we aimed to confirm the hypotheses that were formulated in the first phase. Both phases were performed iteratively. This created the opportunity to improve the data analysis as the study progressed, as well as allowing us to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase.

@@

\begin{table}
       \centering
       \begin{tabular}[ht]{p{3in}}
              \toprule

              \begin{enumerate}
              \item Inspect source code  
              \item Inspect accompanying documentation 
              \item Generate Hypotheses 
              \item Conduct Interview 
              \item Analyse source code 
              \item Analyse interviews 
              \item Classify trends according to types 
              \item Compare classifications against interview responses 
              \item Analyse from software evolution theory point of view 
              \item Validate Hypotheses 
              \end{enumerate} \\
              \bottomrule
       \end{tabular}
       \caption{Methodology Steps}
       \label{table:meth_steps}
\end{table}

@@

%How the initial inspection was performed
The API code was inspected sequentially, starting with v1.4. Both versions of the API underwent the same inspection. This involved extracting method signatures, enums, structs, typedefs and macros, which were subsequently stored in spreadsheets. The extraction involved a lot of manual work, but Git's \cite{git} diff command was used to identify changes in files which exist in both versions. After a change was identified in the code, a description of the corresponding change in the documentation was added to the spreadsheet. The module and file in which the change was identified was then logged together with an ID and a description of the change. The data collection from code and documentation was performed independently by both researchers to reduce the risk of human errors affecting the results. If the data collected by each researcher differed, the cause of the discrepancy was investigated and resolved.

>>>>

\section{Methodology} \label{methodology}
\begin{table}
       \centering
       \begin{tabular}[ht]{p{3in}}
              \toprule

              \textbf{Phase 1: Generate Hypotheses}

              \begin{enumerate}
              \item Inspect source code  
              \item Inspect accompanying documentation 
              \item Generate Hypotheses 
              \item Conduct Interview 
              \item Analyse source code
              \end{enumerate} \\

              \textbf{Phase 2: Confirm Hypotheses}

              \begin{enumerate}
              \item Analyse interviews 
              \item Classify trends according to types 
              \item Compare classifications against interview responses 
              \item Analyse from software evolution theory point of view 
              \item Validate Hypotheses 
              \end{enumerate} \\

              \bottomrule
       \end{tabular}
       \caption{Methodology Steps}
       \label{table:meth_steps}
\end{table}

\section{Methodology} \label{methodology}
\begin{table}
       \centering
       \begin{tabular}[ht]{p{3in}}
              \toprule

              \textbf{Phase 1: Generate Hypotheses}

              \begin{enumerate}
				\item Inspect 1.4
				\item Inspect 2.0
				\item Identify changes between versions
				\item Conduct interview
				\item Structure gathered data
              \end{enumerate} \\

              \textbf{Phase 2: Confirm Hypotheses}

              \begin{enumerate}
              \item Code changes
              \item Group changes
              \item Categorise groups 
              \item Identify and formulate trends
              \item Analyse based on types \cite{chapin2001types}
              \item Analyse based on laws \cite{lehman90sview}
              \end{enumerate} \\

              \bottomrule
       \end{tabular}
       \caption{Methodology Steps}
       \label{table:meth_steps}
\end{table}

%Intro and summary
This study has been conducted using the case study methodology \cite{runeson2009guidelines}. Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis. The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context. The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case, robson2002real, runeson2009guidelines, yin2013case}. An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}. An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of drivers of API change and that input from the industry is vital to the success of the research.

The study was conducted in two major phases \cite{andersson2007spiral}. The aim of the first phase was to generate hypotheses and to formulate clear research questions. This was achieved by using a data-driven approach to analysing the code and documentation. The second phase included analysis of the interviews, during which we aimed to confirm the hypotheses that were formulated in the first phase. Both phases were performed iteratively. This created the opportunity to improve the data analysis as the study progressed, as well as, allowing us to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase.

@@

@@

%How the initial inspection was performed
The API code was inspected sequentially, starting with v1.4. Both versions of the API underwent the same type of inspection. This involved extracting method signatures, enums, structs, typedefs and macros, which were subsequently stored in spreadsheets. The extraction involved a lot of manual work, but Git's \cite{git} diff command was used to identify changes in files which exist in both versions. After a change was identified in the code, a description of the corresponding change in the documentation was added to the spreadsheet. The module and file in which the change was identified was then logged together with an ID and a description of the change. The data collection from code and documentation was performed independently by both researchers to reduce the risk of human errors affecting the results. If the data collected by each researcher differed, the cause of the discrepancy was investigated and resolved.
